%ACKNOLEDGEMENT PAGE
\thispagestyle{empty}
\newpage
\cleardoublepage\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}\index{Acknowledgements}
\begin{center}
{\Large \bf Acknowledgements}\\
\end{center}
\vspace{10pt}
\begin{flushright}
% \textit{“The single greatest cause of happiness is gratitude.” }\\
% \vspace{5mm}
% -Auliq-Ice
\end{flushright}


Behind any major work undertaken by an individual there lies the contribution of the people
who helped him to cross all the hurdles to achieve Her goal. It gives me the immense pleasure to
express my sense of sincere gratitude towards my respected guide \textbf{Prof. Krishna Jariwala},
(Assistant Professor) for Her persistent, outstanding, invaluable co-operation and guidance.It is my
achievement to be guided under him. He is a constant source of encouragement and mo- mentum
that any intricacy becomes simple. I gained a lot of invaluable guidance and prompt suggestions
from him during entire project work. I will be indebted of him forever and I take pride to work
under him. I also express my deep sense of regards and thanks to Professor.Krishna Jariwala, (Pro
fessor and Head of Computer Science Engineering Department). I feel very privileged to have had
their precious advices, guidance and leadership. Last but not the least, my humble thanks to the
Almighty God.


\vspace{1.5cm}
\begin{flushright}
\textbf{Dumpa Bhargav Reddy (200303124205) \\ Dogiparthy V.N.S Srikhar (200303124199) \\ Ayon Karmakar (200303124271) \\ Chirag Gadhvi (200303124212) \\ Parul University, \\ Vadodara}\\ 
\end{flushright}