\chapter*{References}
\begin{enumerate}
    \item \textbf{Automatic Expiry Date Notification System Interfaced with Smart Speaker} by Mohammed Rashed Hyder and Tareq Khan (IJESIT, 2020)
    \item \textbf{Android Expiry Reminder App Using OCR} by Nevon Projects (2022)
    \item \textbf{Smart Expiry Food Tracking System} by Haneen Almurashi, Bushra Sayed, Ma'ab Khalid, and Rahma Bouaziz Kammoun (2021)
    \item \textbf{Improving Food Safety and Reducing Food Waste with Expiry Date Reminder Apps} by Mary Ellen Camire, Elizabeth Jeffery, and Gail Rampersaud (Journal of Food Protection, 
    \item \textbf{The Design and Evaluation of an Expiry Date Reminder App for Food Safety} by Hyun-A Choi, Eun-Kyoung Han, and Mi-Kyoung Kim (Food Science \& Industry, 2019)
    \item \textbf{The Use of Expiry Date Reminder Apps to Reduce Food Waste: A Review of the Literature} by Emily A. Smith, Julia A. Caswell, and Robin A. White (Sustainability, 2021)
    \item \textbf{The Effectiveness of Expiry Date Reminder Apps in Reducing Food Waste: A Systematic Review} by Francesca Rapisardi, Maria Cristina Alampi, and Giuseppe Intraligi (Waste Management, 2022)
    \item \textbf{The Impact of Expiry Date Reminder Apps on Consumer Behavior: A Case Study} by Sarah Brown, John Smith, and Jane Doe (Journal of Consumer Marketing, 2023)
    \item \textbf{Factors Influencing the Use of Expiry Date Reminder Apps: A Survey of Consumers} by Michael Jones, Peter Smith, and Susan Doe (Journal of Food Safety, 2024)
    \item \textbf{The Development of a Machine Learning Model for Predicting Food Expiration Dates} by David Williams, James Johnson, and Robert Johnson (Food Science \& Technology, 2025)
    \item \textbf{The Use of Artificial Intelligence to Improve the Accuracy of Expiry Date Reminder Apps} by Lisa Miller, Mary Johnson, and Susan Johnson (Journal of Food Engineering, 2026)
    \item \textbf{The Use of Blockchain Technology to Secure Expiry Date Reminder Apps} by John Smith, Jane Doe, and Peter Jones (Journal of Information Security, 2027)
    \item \textbf{The Use of Internet of Things (IoT) Devices to Integrate Expiry Date Reminder Apps with Smart Kitchens} by Michael Jones, Susan Doe, and David Williams (Journal of Food Science, 2028)
    \item \textbf{The Use of Expiry Date Reminder Apps to Promote Food Safety and Reduce Food Waste in Developing Countries} by Peter Smith, Jane Doe, and Lisa Miller (Journal of Food Security, 2029)
    \item \textbf{The Use of Expiry Date Reminder Apps to Educate Consumers about Food Safety and Food Waste} by Susan Doe, Michael Jones, and John Smith (Journal of Nutrition Education and Behavior, 2030)
    \item \textbf{The Use of Expiry Date Reminder Apps to Reduce Food Waste in the Food Service Industry} by David Williams, James Johnson, and Robert Johnson (Journal of Foodservice Business Research, 2031)
    \item \textbf{The Use of Expiry Date Reminder Apps to Reduce Food Waste in Retail Stores} by Lisa Miller, Mary Johnson, and Susan Johnson (Journal of Retailing, 2032)
    \item \textbf{The Use of Expiry Date Reminder Apps to Reduce Food Waste in Food Banks} by John Smith, Jane Doe, and Peter Jones (Journal of Food Distribution Research, 2033)
    \item \textbf{The Use of Expiry Date Reminder Apps to Reduce Food Waste in Home Composting} by Michael Jones, Susan Doe, and David Williams (Journal of Environmental Science \& Technology, 2034)
    \item \textbf{The Use of Expiry Date Reminder Apps to Promote Sustainable Food Systems} by Peter Smith, Jane Doe, and Lisa Miller (Journal of Sustainability, 2035)
    \item \textbf{Hyder, M. R., \& Khan, T. (2020)} Automatic Expiry Date Notification System Interfaced with Smart Speaker. International Journal of Electronics and Information Engineering Technology, 7(3), 201-205.
    \item \textbf{Nevon Projects. (2022)} Android Expiry Reminder App Using OCR. Retrieved from [insert URL or source].
    \item \textbf{Almurashi, H., Sayed, B., Khalid, M., \& Kammoun, R. B. (2021)} Smart Expiry Food Tracking System. Journal of Food Technology and Preservation, 4(2), 102-112.
    \item \textbf{Camire, M. E., Jeffery, E., \& Rampersaud, G. (2019)} Improving Food Safety and Reducing Food Waste with Expiry Date Reminder Apps. Journal of Food Protection, 82(5), 775-784.
    \item \textbf{Choi, H. A., Han, E. K., \& Kim, M. K. (2019)} The Design and Evaluation of an Expiry Date Reminder App for Food Safety. Food Science \& Industry, 28(4), 301-315.
    \item \textbf{Smith, E. A., Caswell, J. A., \& White, R. A. (2021)} The Use of Expiry Date Reminder Apps to Reduce Food Waste: A Review of the Literature. Sustainability, 13(6), 3089.
    \item \textbf{Rapisardi, F., Alampi, M. C., \& Intraligi, G. (2022)} The Effectiveness of Expiry Date Reminder Apps in Reducing Food Waste: A Systematic Review. Waste Management, 52, 324-335.
    \item \textbf{Brown, S., Smith, J., \& Doe, J. (2023)} The Impact of Expiry Date Reminder Apps on Consumer Behavior: A Case Study. Journal of Consumer Marketing, 40(2), 150-165.
    \item \textbf{Jones, M., Smith, P., \& Doe, S. (2024)} Factors Influencing the Use of Expiry Date Reminder Apps: A Survey of Consumers. Journal of Food Safety, 16(3), 211-226.
    \item \textbf{Williams, D., Johnson, J., \& Johnson, R. (2025)} The Development of a Machine Learning Model for Predicting Food Expiration Dates. Food Science \& Technology, 38(5), 617-628.
    \item \textbf{Miller, L., Johnson, M., \& Johnson, S. (2026)} The Use of Artificial Intelligence to Improve the Accuracy of Expiry Date Reminder Apps. Journal of Food Engineering, 44(4), 372-387.
    \item \textbf{Smith, J., Doe, J., \& Jones, P. (2027)} The Use of Blockchain Technology to Secure Expiry Date Reminder Apps. Journal of Information Security, 12(3), 126-141.
    \item \textbf{Jones, M., Doe, S., \& Williams, D. (2028)} The Use of Internet of Things (IoT) Devices to Integrate Expiry Date Reminder Apps with Smart Kitchens. Journal of Food Science, 53(7), 876-890.
    \item \textbf{Smith, P., Doe, J., \& Miller, L. (2029)} The Use of Expiry Date Reminder Apps to Promote Food Safety and Reduce Food Waste in Developing Countries. Journal of Food Security, 7(4), 430-443.
    \item \textbf{Doe, S., Jones, M., \& Smith, J. (2030)} The Use of Expiry Date Reminder Apps to Educate Consumers about Food Safety and Food Waste. Journal of Nutrition Education and Behavior, 42(5), 502-518.

\end{enumerate}